Determinism, Complexity, and Predictability in Computer Performance

### 2014-02-10 pecomplexity.tex
add better captions

This primary finding: ``Signals that are more complex are harder to predict." At
first glance this finding may seem incredibly trivial, of course a complex
signal is harder to predict than a trivial one, but this is \emph{not} the core
result here as we will elucidate now with Figure \ref{fig:predictions_vs_wpe}.
\begin{figure}[htbp]
  \centering
  \begin{subfigure}{0.5\textwidth}
    \includegraphics[width=1.0\textwidth]{figs/LMA_prediction_vs_entropy}
    \caption{The MASE of LMA vs weighted permutation entropy. For each of these,
    the word length used is $6$.}
    \label{fig:lma_pred_vs_wpe}
  \end{subfigure}%
  \begin{subfigure}{0.5\textwidth}
    \includegraphics[width=1.0\textwidth]{figs/ARIMA_prediction_vs_entropy}
    \caption{The MASE of ARIMA vs weighted permutation entropy. For each of
    these, the word length used is $6$.}
    \label{fig:arima_pred_vs_wpe}
  \end{subfigure}
  % \begin{subfigure}{0.5\textwidth}
  %   \includegraphics[width=1.0\textwidth]{figs/LMA_vs_ARIMA}
  %   \caption{The MASE values for LMA against ARIMA. The dashed line is the
  %   identity, delineating the traces for which either LMA or ARIMA performed
  %   better. All traces except those from {\tt SVD$_1$} lie above the line,
  %   indicating that LMA is better suited prediction method for the computer
  %  traces considered.}\label{fig:lma_vs_arima}
  % \end{subfigure}
  \label{fig:predictions_vs_wpe}
\end{figure}

>>>>

This primary finding: ``Signals that are more complex are harder to predict." At
first glance this finding may seem incredibly trivial, of course a complex
signal is harder to predict than a trivial one, but this is \emph{not} the core
result here as we will elucidate now with Figure \ref{fig:predictions_vs_wpe}.
\begin{figure}[htbp]
  \centering
  \begin{subfigure}[t]{0.5\textwidth}
    \includegraphics[width=1.0\textwidth]{figs/LMA_prediction_vs_entropy}
    \caption{The MASE of LMA vs weighted permutation entropy. For each of these,
    the word length used is $6$. Prediction error vs WPE values largely fall
    near the fit from Fig.~\ref{fig:pred_vs_wpe} indicating that LMA is a near-
    optimal prediction method for this data.}
    \label{fig:lma_pred_vs_wpe}
  \end{subfigure}%
  \begin{subfigure}[t]{0.5\textwidth}
    \includegraphics[width=1.0\textwidth]{figs/ARIMA_prediction_vs_entropy}
    \caption{The MASE of ARIMA vs weighted permutation entropy. For each of
    these, the word length used is $6$. Prediction error vs WPE values for many
    of the traces fall far to the right of the fit from
    Fig.~\ref{fig:pred_vs_wpe} indicating that ARIMA is a poor choice to predict
    this data.}
    \label{fig:arima_pred_vs_wpe}
  \end{subfigure}
  % \begin{subfigure}{0.5\textwidth}
  %   \includegraphics[width=1.0\textwidth]{figs/LMA_vs_ARIMA}
  %   \caption{The MASE values for LMA against ARIMA. The dashed line is the
  %   identity, delineating the traces for which either LMA or ARIMA performed
  %   better. All traces except those from {\tt SVD$_1$} lie above the line,
  %   indicating that LMA is better suited prediction method for the computer
  %  traces considered.}\label{fig:lma_vs_arima}
  % \end{subfigure}
  \label{fig:predictions_vs_wpe}
\end{figure}
